Migration Experience Trajectories: Subtitle TBD

### 2022-05-12 preregistration/Preregistration3MPCA.Rmd
typo

Two important developments, within the psychological sciences in general and in inter-ethnic/migrantion research in particular, have been (1) a shift towards more comprehensive assessment of human experiences and (2) a growing focus on longitudinal real-life data. For the migration research field, recent reviews have been pushing for models that take into account affects, behaviors, cognitions, and desires when it comes to migrant adaptations [@Kreienkamp2022d, @Ward2019, @Cottam2010, @Hogg2005, @Jhangiani2014].
At the same time prominent figures in the field have called for studies that collect longitudinal [@Pettigrew1998, @Pettigrew2008, @Pettigrew2008b, @Pettigrew2011] and real-life experience-sampling data outside the lab [@MacInnis2015, @McKeown2017, @Dixon2005].

@@

* data collection possible (e.g., ContactLogger [@Keil2020], FormR [@Arslan2020])
* analyses become more accessible [@ODonnell2021]

>>>>

Two important developments, within the psychological sciences in general and in migration research in particular, have been (1) a shift towards more comprehensive assessment of human experiences and (2) a growing focus on longitudinal real-life data. 
For the migration research field, recent reviews have been pushing for models that take into account affects, behaviors, cognitions, and desires when it comes to migrant adaptations [@Kreienkamp2022d; @Ward2019; @Cottam2010; @Hogg2005; @Jhangiani2014]. At the same time prominent figures in the field have called for studies that collect longitudinal [@Pettigrew1998; @Pettigrew2008; @Pettigrew2008b; @Pettigrew2011] and real-life experience-sampling data outside the lab [@MacInnis2015; @McKeown2017; @Dixon2005].

@@
